### 2017-07-28 manuscript.tex
upload fig 1 draft and add results subsection headers

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
There is great interest in broad antibody-based immunity against influenza virus.
Even for antibodies recognizing broad swaths of influenza strains, viral genetic variation can influence neutralization sensitivity.
To better understand the potential for viral resistance to antibodies, there is a need to evaluate not just whether mutations can influence sensitivity to an antibody, but rather to comprehensively quantify how many mutations do this and by how much, and to make these comparisons across antibodies.
Here we comprehensively map mutations that increase viral resistance to the broadly neutralizing anti-influenza antibodies FI6v3, C179, and S139/1, and compare the results to those previously obtained for narrow strain-specific antibodies.
We find that although there are some mutations that enhance resistance to the stalk-binding antibody FI6v3 \comment{and C179?}, these mutations are both rare and modest in their effect sizes.
\comment{..?... In contrast, viral escape from S139/1 ... looks more like the narrow head binders than the broad stalk binders?}
We formalize these observations into a framework for quantitative comparison of viral escape potential between different antibodies.
Overall, our work demonstrates that a virus's absolute capacity to escape an antibody can be quantified, and that influenza is in fact extremely limited in its ability to escape some antibodies \comment{targeting the stalk... and also extremely adept at escaping another broadly-reactive antibody targeting the head... }.

@@

\subsection*{Results subsection 1}

\subsection*{Results subsection 2}

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
There is great interest in broad antibody-based immunity against influenza virus.
Even for antibodies recognizing broad swaths of influenza strains, viral genetic variation can influence neutralization sensitivity.
To better understand the potential for viral resistance to antibodies, there is a need to evaluate not just whether mutations can influence sensitivity to an antibody, but rather to comprehensively quantify how many mutations do this and by how much, and to make these comparisons across antibodies.
Here we comprehensively map mutations that increase viral resistance to the broadly neutralizing anti-influenza antibodies FI6v3, C179, and S139/1, and compare the results to those previously obtained for narrow strain-specific antibodies.
We find that although there are some mutations that enhance resistance to the stalk-binding antibody FI6v3 and C179, these mutations are both rare and modest in their effect sizes.
\comment{..?... In contrast, viral escape from S139/1 ... looks more like the narrow head binders than the broad stalk binders?}
We formalize these observations into a framework for quantitative comparison of viral escape potential between different antibodies.
Overall, our work demonstrates that a virus's absolute capacity to escape an antibody can be quantified, and that influenza is in fact extremely limited in its ability to escape some antibodies \comment{targeting the stalk... and also extremely adept at escaping another broadly-reactive antibody targeting the head... }.

@@

\subsection*{Characterizing escape mutations from a broadly neutralizing receptor site binding antibody}

\subsection*{Characterizing escape mutations from broadly neutralizing stalk-binding antibodies}

\subsection*{Comparison of escape profiles with mutational tolerance}

\subsection*{Quantitatively comparing escape from different neutralizing antibodies}
